%-------------------------
% Resume in Latex
% Author : Tim Myers
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{needspace}

\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Define custom colors
\definecolor{primary}{RGB}{70, 130, 180} % Steel Blue
\definecolor{linkcolor}{RGB}{39, 174, 96} % Green color for links

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{primary}
}{}{0em}{}[\color{primary}\titlerule \vspace{-5pt}]

% Customize hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,
    urlcolor=linkcolor,
    pdftitle={Tim Myers - Resume},
    pdfauthor={Tim Myers},
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBold}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[3]{
  \needspace{4\baselineskip}\vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{primary}#1} \\
      \textit{\small#2} & \textit{\small #3} \\
    \end{tabular*}\vspace{-5pt}
}

% Compact skills line: \resumeSkill{Category}{items}
\newcommand{\resumeSkill}[2]{\item\small{\textbf{\color{primary}#1:} #2}\vspace{-3pt}}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSkillListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeSkillListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://resume.tmye.me/}{\Large \color{primary}Tim Myers}} &
  \href{mailto:timmyers09@gmail.com}{timmyers09@gmail.com} \\
  \textit{\small Principal Platform \& Infrastructure Engineer} &
  \href{https://resume.tmye.me/}{https://resume.tmye.me} \\
\end{tabular*}


%-----------SUMMARY-----------------
\section{Summary}
\vspace{3pt}
\small{
Principal software \& platform engineer with 10+ years building high-throughput backend services and operating cloud infrastructure at scale. Expert in infrastructure-as-code, Kubernetes, and CI/CD, with a track record of modernizing DevOps and reliability across blockchain, fintech, and connected-device companies. Early, hands-on adopter of agentic AI coding harnesses, embedding automated implementation, review, and QA into the delivery pipeline to ship faster at higher quality.
}
\vspace{2pt}


%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeSkillListStart
    \resumeSkill{Cloud \& Infrastructure}{AWS, Terraform, Infrastructure as Code}
    \resumeSkill{Containers \& Orchestration}{Kubernetes (custom operators), Docker, CI/CD}
    \resumeSkill{Languages}{Go, TypeScript, JavaScript, Python}
    \resumeSkill{Backend \& Data}{Microservices, serverless \& event-driven (AWS Lambda), REST APIs, multi-layer caching, Postgres, DynamoDB}
    \resumeSkill{AI \& Developer Tooling}{Claude Code / agentic coding harnesses, AI-driven code review \& QA, AI-in-the-loop CI/CD}
  \resumeSkillListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Invent Money}
      {Senior Engineer / SRE}{Nov 2025 - May 2026}
      \resumeItemListStart
        \resumeItemNoBold {Pioneered adoption of agentic AI coding harnesses (Claude Code) across application code and infrastructure, embedding automated code review and QA into the development lifecycle to accelerate delivery while raising quality.}
        \resumeItemNoBold {Built an end-to-end pipeline that turns a well-defined Linear issue into shipped code with a single command --- implementing, testing, opening and merging the PR, resolving AI code-review feedback, and running post-merge acceptance tests.}
        \resumeItemNoBold {Led the migration of all production infrastructure from Railway to AWS, managing the entire footprint as code with reproducible environments and automated provisioning.}
      \resumeItemListEnd

    \resumeSubheading
      {Bendy}
      {Founder \& Solo Engineer --- mobility-focused fitness app (\href{https://bendy.fit}{bendy.fit})}{Jan 2025 - Present}
      \resumeItemListStart
        \resumeItemNoBold {Designing and building a mobility-focused fitness app end-to-end as sole engineer --- product, cross-platform mobile client, backend services, and cloud infrastructure.}
        \resumeItemNoBold {Own the full stack and delivery pipeline solo, leveraging AI coding harnesses to ship at the velocity of a small team.}
      \resumeItemListEnd

    \resumeSubheading
      {ConsenSys (Infura)}
      {Principal Software Engineer}{Mar 2019 - Oct 2024}
      \resumeItemListStart
        \resumeItemNoBold {Built and operated core backend services behind Infura's products --- high-throughput Ethereum API accelerators, account management, billing and usage metering, authentication, API design and versioning, and multi-layer caching.}
        \resumeItemNoBold {Designed and shipped a custom Kubernetes operator managing the full lifecycle of blockchain nodes, enabling rapid onboarding of new networks and the products built on top of them.}
        \resumeItemNoBold {Modernized Infura's DevOps and CI/CD --- integrating automation and streamlining pipelines to improve operational efficiency and scalability.}
        \resumeItemNoBold {Spearheaded Infura's Decentralized Infrastructure Network (DIN), applying lessons learned operating multi-network support at scale.}
      \resumeItemListEnd

    \resumeSubheading
      {ShapeShift}
      {Senior SRE / DevOps Engineer}{May 2018 - Mar 2019}
      \resumeItemListStart
        \resumeItemNoBold {Eliminated infrastructure waste, saving tens of thousands of dollars and hundreds of engineering hours every month.}
        \resumeItemNoBold {Overhauled infrastructure and DevOps practices with infrastructure-as-code, containers, and modern tooling.}
      \resumeItemListEnd

    \resumeSubheading
      {Closetbox}
      {Senior Software Engineer}{Sep 2017 - May 2018}
      \resumeItemListStart
        \resumeItemNoBold {Converted a monolith into serverless, event-driven microservices on AWS Lambda, significantly improving scalability and developer velocity.}
        \resumeItemNoBold {Took on the DevOps role --- moving infrastructure to code with Terraform and building full CI/CD pipelines from scratch with Docker and CircleCI.}
      \resumeItemListEnd

    \resumeSubheading
      {Josh.ai}
      {Senior Software Architect --- Tools and Infrastructure}{Aug 2015 - Sep 2017}
      \resumeItemListStart
        \resumeItemNoBold {Designed and implemented a real-time streaming data synchronization protocol keeping iOS, Android, and Web clients in sync with the state of the home.}
        \resumeItemNoBold {Wrote device drivers integrating dozens of smart-home ecosystems (Lutron, Crestron, Control4, LIFX, Philips Hue, and more).}
        \resumeItemNoBold {Led front-end development in React and React Native, sharing 95\% of code across Web, Android, and iOS from a single codebase.}
      \resumeItemListEnd

    \resumeSubheading
      {NetApp}
      {Firmware Engineer}{Jul 2014 - Jul 2015}
      \resumeItemListStart
        \resumeItemNoBold {Implemented firmware for a cloud backup service for storage arrays, delivering off-site disaster recovery and data restore to customers without a second datacenter.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Boulder}
      {Master's Degree, Electrical Engineering, GPA: 4.0}{Sep 2013 - May 2014}

    \resumeSubheading
      {University of Colorado Boulder}
      {Bachelor's Degree, Electrical and Computer Engineering, GPA: 3.9}{Sep 2009 - May 2013}
  \resumeSubHeadingListEnd
\end{document}
